More than one Author with different Affiliations

### 2016-04-08 NatPlant2/manuscript.tex
updates

\section*{ONLINE METHODS}
\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
%\bibliographystyle{NatureSeriesT}
\bibliography{Reference}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\onecolumn
\input{supportingInfo}

>>>>

\section*{METHODS}
\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
%\bibliographystyle{naturemag}
%\bibliography{Reference}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{dobzhansky1957}
\bibinfo{author}{Dobzhansky, T.} \& \bibinfo{author}{Pavlovsky, O.}
\newblock \bibinfo{title}{An experimental study of interaction between genetic
  drift and natural selection}.
\newblock \emph{\bibinfo{journal}{Evolution}} \bibinfo{pages}{311--319}
  (\bibinfo{year}{1957}).

\bibitem{voight2005}
\bibinfo{author}{Voight, B.~F.} \emph{et~al.}
\newblock \bibinfo{title}{Interrogating multiple aspects of variation in a full
  resequencing data set to infer human population size changes}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{102}},
  \bibinfo{pages}{18508--18513} (\bibinfo{year}{2005}).

\bibitem{luikart2003}
\bibinfo{author}{Luikart, G.}, \bibinfo{author}{England, P.~R.},
  \bibinfo{author}{Tallmon, D.}, \bibinfo{author}{Jordan, S.} \&
  \bibinfo{author}{Taberlet, P.}
\newblock \bibinfo{title}{The power and promise of population genomics: from
  genotyping to genome typing}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Genetics}}
  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{981--994}
  (\bibinfo{year}{2003}).

\bibitem{gutenkunst2009}
\bibinfo{author}{Gutenkunst, R.~N.}, \bibinfo{author}{Hernandez, R.~D.},
  \bibinfo{author}{Williamson, S.~H.} \& \bibinfo{author}{Bustamante, C.~D.}
\newblock \bibinfo{title}{Inferring the joint demographic history of multiple
  populations from multidimensional snp frequency data}.
\newblock \emph{\bibinfo{journal}{PLoS genetics}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{e1000695} (\bibinfo{year}{2009}).

\bibitem{akey2009}
\bibinfo{author}{Akey, J.~M.}
\newblock \bibinfo{title}{Constructing genomic maps of positive selection in
  humans: Where do we go from here?}
\newblock \emph{\bibinfo{journal}{Genome research}}
  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{711--722}
  (\bibinfo{year}{2009}).

\bibitem{smith1974}
\bibinfo{author}{Smith, J.~M.} \& \bibinfo{author}{Haigh, J.}
\newblock \bibinfo{title}{The hitch-hiking effect of a favourable gene}.
\newblock \emph{\bibinfo{journal}{Genetical research}}
  \textbf{\bibinfo{volume}{23}}, \bibinfo{pages}{23--35}
  (\bibinfo{year}{1974}).

\bibitem{li2012}
\bibinfo{author}{Li, J.} \emph{et~al.}
\newblock \bibinfo{title}{Joint analysis of demography and selection in
  population genetics: where do we stand and where could we go?}
\newblock \emph{\bibinfo{journal}{Molecular Ecology}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{28--44}
  (\bibinfo{year}{2012}).

\bibitem{slotte2014}
\bibinfo{author}{Slotte, T.}
\newblock \bibinfo{title}{The impact of linked selection on plant genomic
  variation}.
\newblock \emph{\bibinfo{journal}{Briefings in functional genomics}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{268--275}
  (\bibinfo{year}{2014}).

\bibitem{charlesworth1993}
\bibinfo{author}{Charlesworth, B.}, \bibinfo{author}{Morgan, M.} \&
  \bibinfo{author}{Charlesworth, D.}
\newblock \bibinfo{title}{The effect of deleterious mutations on neutral
  molecular variation.}
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{134}},
  \bibinfo{pages}{1289--1303} (\bibinfo{year}{1993}).

\bibitem{sella2009}
\bibinfo{author}{Sella, G.}, \bibinfo{author}{Petrov, D.~A.},
  \bibinfo{author}{Przeworski, M.} \& \bibinfo{author}{Andolfatto, P.}
\newblock \bibinfo{title}{Pervasive natural selection in the drosophila
  genome?}
\newblock \emph{\bibinfo{journal}{PLoS genetics}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{e1000495} (\bibinfo{year}{2009}).

\bibitem{elyashiv2014}
\bibinfo{author}{Elyashiv, E.} \emph{et~al.}
\newblock \bibinfo{title}{A genomic map of the effects of linked selection in
  drosophila}.
\newblock \emph{\bibinfo{journal}{arXiv preprint arXiv:1408.5461}}
  (\bibinfo{year}{2014}).

\bibitem{andolfatto2005}
\bibinfo{author}{Andolfatto, P.}
\newblock \bibinfo{title}{Adaptive evolution of non-coding dna in drosophila}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{437}},
  \bibinfo{pages}{1149--1152} (\bibinfo{year}{2005}).

\bibitem{cutter2013}
\bibinfo{author}{Cutter, A.~D.} \& \bibinfo{author}{Payseur, B.~A.}
\newblock \bibinfo{title}{Genomic signatures of selection at linked sites:
  unifying the disparity among species}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Genetics}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{262--274}
  (\bibinfo{year}{2013}).

\bibitem{corbett2015}
\bibinfo{author}{Corbett-Detig, R.~B.}, \bibinfo{author}{Hartl, D.~L.} \&
  \bibinfo{author}{Sackton, T.~B.}
\newblock \bibinfo{title}{Natural selection constrains neutral diversity across
  a wide range of species}.
\newblock \emph{\bibinfo{journal}{PLoS Biol}} \textbf{\bibinfo{volume}{13}},
  \bibinfo{pages}{e1002112} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{http://dx.doi.org/10.1371%2Fjournal.pbio.1002112}.

\bibitem{leffler2012}
\bibinfo{author}{Leffler, E.~M.} \emph{et~al.}
\newblock \bibinfo{title}{Revisiting an old riddle: what determines genetic
  diversity levels within species}.
\newblock \emph{\bibinfo{journal}{PLoS Biol}} \textbf{\bibinfo{volume}{10}},
  \bibinfo{pages}{e1001388} (\bibinfo{year}{2012}).

\bibitem{duchen2013}
\bibinfo{author}{Duchen, P.}, \bibinfo{author}{{\v{Z}}ivkovi{\'c}, D.},
  \bibinfo{author}{Hutter, S.}, \bibinfo{author}{Stephan, W.} \&
  \bibinfo{author}{Laurent, S.}
\newblock \bibinfo{title}{Demographic inference reveals african and european
  admixture in the north american drosophila melanogaster population}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{193}},
  \bibinfo{pages}{291--301} (\bibinfo{year}{2013}).

\bibitem{reich1998}
\bibinfo{author}{Reich, D.~E.} \& \bibinfo{author}{Goldstein, D.~B.}
\newblock \bibinfo{title}{Genetic evidence for a paleolithic human population
  expansion in africa}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{95}}, \bibinfo{pages}{8119--8123}
  (\bibinfo{year}{1998}).

\bibitem{hyten2006}
\bibinfo{author}{Hyten, D.~L.} \emph{et~al.}
\newblock \bibinfo{title}{Impacts of genetic bottlenecks on soybean genome
  diversity}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{103}}, \bibinfo{pages}{16666--16671}
  (\bibinfo{year}{2006}).

\bibitem{bovine2009}
\bibinfo{author}{Consortium, B.~H.} \emph{et~al.}
\newblock \bibinfo{title}{Genome-wide survey of snp variation uncovers the
  genetic structure of cattle breeds}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{324}},
  \bibinfo{pages}{528--532} (\bibinfo{year}{2009}).

\bibitem{ellegren2014}
\bibinfo{author}{Ellegren, H.}
\newblock \bibinfo{title}{Genome sequencing and population genomics in
  non-model organisms}.
\newblock \emph{\bibinfo{journal}{Trends in ecology \& evolution}}
  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{51--63}
  (\bibinfo{year}{2014}).

\bibitem{smith1995}
\bibinfo{author}{Smith, B.~D.}
\newblock \emph{\bibinfo{title}{The emergence of agriculture}}
  (\bibinfo{publisher}{Scientific American Library New York},
  \bibinfo{year}{1995}).

\bibitem{matsuoka2002}
\bibinfo{author}{Matsuoka, Y.} \emph{et~al.}
\newblock \bibinfo{title}{A single domestication for maize shown by multilocus
  microsatellite genotyping}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{99}}, \bibinfo{pages}{6080--6084}
  (\bibinfo{year}{2002}).

\bibitem{wright2005}
\bibinfo{author}{Wright, S.~I.} \emph{et~al.}
\newblock \bibinfo{title}{The effects of artificial selection on the maize
  genome}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{308}},
  \bibinfo{pages}{1310--1314} (\bibinfo{year}{2005}).

\bibitem{eyre1998}
\bibinfo{author}{Eyre-Walker, A.}, \bibinfo{author}{Gaut, R.~L.},
  \bibinfo{author}{Hilton, H.}, \bibinfo{author}{Feldman, D.~L.} \&
  \bibinfo{author}{Gaut, B.~S.}
\newblock \bibinfo{title}{Investigation of the bottleneck leading to the
  domestication of maize}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{95}}, \bibinfo{pages}{4441--4446}
  (\bibinfo{year}{1998}).

\bibitem{tenaillon2004}
\bibinfo{author}{Tenaillon, M.~I.}, \bibinfo{author}{U'Ren, J.},
  \bibinfo{author}{Tenaillon, O.} \& \bibinfo{author}{Gaut, B.~S.}
\newblock \bibinfo{title}{Selection versus demography: a multilocus
  investigation of the domestication process in maize}.
\newblock \emph{\bibinfo{journal}{Molecular Biology and Evolution}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{1214--1225}
  (\bibinfo{year}{2004}).

\bibitem{chia2012}
\bibinfo{author}{Chia, J.-M.} \emph{et~al.}
\newblock \bibinfo{title}{Maize hapmap2 identifies extant variation from a
  genome in flux}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{803--807}
  (\bibinfo{year}{2012}).

\bibitem{bukowski2015}
\bibinfo{author}{Bukowski, R.} \emph{et~al.}
\newblock \bibinfo{title}{Construction of the third generation zea mays
  haplotype map}.
\newblock \emph{\bibinfo{journal}{bioRxiv}} \bibinfo{pages}{026963}
  (\bibinfo{year}{2015}).

\bibitem{hufford2012}
\bibinfo{author}{Hufford, M.~B.} \emph{et~al.}
\newblock \bibinfo{title}{Comparative population genomics of maize
  domestication and improvement}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{808--811}
  (\bibinfo{year}{2012}).

\bibitem{ewing2016}
\bibinfo{author}{Ewing, G.~B.} \& \bibinfo{author}{Jensen, J.~D.}
\newblock \bibinfo{title}{The consequences of not accounting for background
  selection in demographic inference}.
\newblock \emph{\bibinfo{journal}{Molecular ecology}}
  \textbf{\bibinfo{volume}{25}}, \bibinfo{pages}{135--141}
  (\bibinfo{year}{2016}).

\bibitem{Hearne2015}
\bibinfo{author}{Hearne, S.}, \bibinfo{author}{Chen, C.},
  \bibinfo{author}{Buckler, E.} \& \bibinfo{author}{Mitchell, S.}
\newblock \bibinfo{title}{Unimputed gbs derived snps for maize landrace
  accessions represented in the seed-maize gwas panel}.
\newblock \bibinfo{howpublished}{\url{http://hdl.handle.net/11529/10034}}
  (\bibinfo{year}{2015}).
\newblock \bibinfo{note}{Accessed: 2015-02-16}.

\bibitem{keinan2012}
\bibinfo{author}{Keinan, A.} \& \bibinfo{author}{Clark, A.~G.}
\newblock \bibinfo{title}{Recent explosive human population growth has resulted
  in an excess of rare genetic variants}.
\newblock \emph{\bibinfo{journal}{science}} \textbf{\bibinfo{volume}{336}},
  \bibinfo{pages}{740--743} (\bibinfo{year}{2012}).

\bibitem{fu1993}
\bibinfo{author}{Fu, Y.-X.} \& \bibinfo{author}{Li, W.-H.}
\newblock \bibinfo{title}{Statistical tests of neutrality of mutations.}
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{133}},
  \bibinfo{pages}{693--709} (\bibinfo{year}{1993}).

\bibitem{clark2005}
\bibinfo{author}{Clark, R.~M.}, \bibinfo{author}{Tavar{\'e}, S.} \&
  \bibinfo{author}{Doebley, J.}
\newblock \bibinfo{title}{Estimating a nucleotide substitution rate for maize
  from polymorphism at a major domestication locus}.
\newblock \emph{\bibinfo{journal}{Molecular biology and evolution}}
  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{2304--2312}
  (\bibinfo{year}{2005}).

\bibitem{schiffels2014}
\bibinfo{author}{Schiffels, S.} \& \bibinfo{author}{Durbin, R.}
\newblock \bibinfo{title}{Inferring human population size and separation
  history from multiple genome sequences}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}  (\bibinfo{year}{2014}).

\bibitem{wang2005}
\bibinfo{author}{Wang, H.} \emph{et~al.}
\newblock \bibinfo{title}{The origin of the naked grains of maize}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{436}},
  \bibinfo{pages}{714--719} (\bibinfo{year}{2005}).

\bibitem{wang2015}
\bibinfo{author}{Wang, H.}, \bibinfo{author}{Studer, A.~J.},
  \bibinfo{author}{Zhao, Q.}, \bibinfo{author}{Meeley, R.} \&
  \bibinfo{author}{Doebley, J.~F.}
\newblock \bibinfo{title}{Evidence that the origin of naked kernels during
  maize domestication was caused by a single amino acid substitution in tga1}.
\newblock \emph{\bibinfo{journal}{Genetics}} \bibinfo{pages}{genetics--115}
  (\bibinfo{year}{2015}).

\bibitem{enard2014}
\bibinfo{author}{Enard, D.}, \bibinfo{author}{Messer, P.~W.} \&
  \bibinfo{author}{Petrov, D.~A.}
\newblock \bibinfo{title}{Genome-wide signals of positive selection in human
  evolution}.
\newblock \emph{\bibinfo{journal}{Genome research}}
  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{885--895}
  (\bibinfo{year}{2014}).

\bibitem{rodgers2015}
\bibinfo{author}{Rodgers-Melnick, E.} \emph{et~al.}
\newblock \bibinfo{title}{Recombination in diverse maize is stable,
  predictable, and associated with genetic load}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{3823--3828}
  (\bibinfo{year}{2015}).

\bibitem{davydov2010}
\bibinfo{author}{Davydov, E.~V.} \emph{et~al.}
\newblock \bibinfo{title}{Identifying a high fraction of the human genome to be
  under selective constraint using gerp++}.
\newblock \emph{\bibinfo{journal}{PLoS Comput Biol}}
  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{e1001025}
  (\bibinfo{year}{2010}).

\bibitem{tenaillon2002}
\bibinfo{author}{Tenaillon, M.~I.} \emph{et~al.}
\newblock \bibinfo{title}{Patterns of diversity and recombination along
  chromosome 1 of maize (zea mays ssp. mays l.)}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{162}},
  \bibinfo{pages}{1401--1413} (\bibinfo{year}{2002}).

\bibitem{innan2004}
\bibinfo{author}{Innan, H.} \& \bibinfo{author}{Kim, Y.}
\newblock \bibinfo{title}{Pattern of polymorphism after strong artificial
  selection in a domestication event}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{101}},
  \bibinfo{pages}{10667--10672} (\bibinfo{year}{2004}).

\bibitem{messer2013}
\bibinfo{author}{Messer, P.~W.} \& \bibinfo{author}{Petrov, D.~A.}
\newblock \bibinfo{title}{Population genomics of rapid adaptation by soft
  selective sweeps}.
\newblock \emph{\bibinfo{journal}{Trends in ecology \& evolution}}
  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{659--669}
  (\bibinfo{year}{2013}).

\bibitem{garud2015}
\bibinfo{author}{Garud, N.~R.}, \bibinfo{author}{Messer, P.~W.},
  \bibinfo{author}{Buzbas, E.~O.} \& \bibinfo{author}{Petrov, D.~A.}
\newblock \bibinfo{title}{Recent selective sweeps in north american drosophila
  melanogaster show signatures of soft sweeps}.
\newblock \emph{\bibinfo{journal}{PLoS genetics}}
  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{e1005004}
  (\bibinfo{year}{2015}).

\bibitem{piperno2009}
\bibinfo{author}{Piperno, D.~R.}, \bibinfo{author}{Ranere, A.~J.},
  \bibinfo{author}{Holst, I.}, \bibinfo{author}{Iriarte, J.} \&
  \bibinfo{author}{Dickau, R.}
\newblock \bibinfo{title}{Starch grain and phytolith evidence for early ninth
  millennium bp maize from the central balsas river valley, mexico}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{106}}, \bibinfo{pages}{5019--5024}
  (\bibinfo{year}{2009}).

\bibitem{cimmyt1999}
\bibinfo{author}{Program, T.~M.}
\newblock \emph{\bibinfo{title}{Development, maintenance, and seed
  multiplication of open-pollinated maize varieties}}
  (\bibinfo{publisher}{CIMMYT}, \bibinfo{address}{Mexico, D.F.},
  \bibinfo{year}{1999}), \bibinfo{edition}{2} edn.

\bibitem{baden2001}
\bibinfo{author}{Baden, W.~W.} \& \bibinfo{author}{Beekman, C.~S.}
\newblock \bibinfo{title}{Culture and agriculture: A comment on sissel
  schroeder, maize productivity in the eastern woodlands and great plains of
  north america}.
\newblock \emph{\bibinfo{journal}{American Antiquity}}
  \bibinfo{pages}{505--515} (\bibinfo{year}{2001}).

\bibitem{studer2011}
\bibinfo{author}{Studer, A.}, \bibinfo{author}{Zhao, Q.},
  \bibinfo{author}{Ross-Ibarra, J.} \& \bibinfo{author}{Doebley, J.}
\newblock \bibinfo{title}{Identification of a functional transposon insertion
  in the maize domestication gene tb1}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}
  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{1160--1163}
  (\bibinfo{year}{2011}).

\bibitem{gallavotti2004role}
\bibinfo{author}{Gallavotti, A.} \emph{et~al.}
\newblock \bibinfo{title}{The role of barren stalk1 in the architecture of
  maize}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{432}},
  \bibinfo{pages}{630--635} (\bibinfo{year}{2004}).

\bibitem{wills2013}
\bibinfo{author}{Wills, D.~M.} \emph{et~al.}
\newblock \bibinfo{title}{From many, one: genetic control of prolificacy during
  maize domestication}.
\newblock \emph{\bibinfo{journal}{PLoS Genet}} \textbf{\bibinfo{volume}{9}},
  \bibinfo{pages}{e1003604} (\bibinfo{year}{2013}).

\bibitem{Takuno15062015}
\bibinfo{author}{Takuno, S.} \emph{et~al.}
\newblock \bibinfo{title}{Independent molecular basis of convergent highland
  adaptation in maize}.
\newblock \emph{\bibinfo{journal}{Genetics}}  (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{http://www.genetics.org/content/early/2015/06/15/genetics.115.178327.abstract}.
\newblock
  \eprint{http://www.genetics.org/content/early/2015/06/15/genetics.115.178327.full.pdf+html}.

\bibitem{van2012historical}
\bibinfo{author}{van Heerwaarden, J.}, \bibinfo{author}{Hufford, M.~B.} \&
  \bibinfo{author}{Ross-Ibarra, J.}
\newblock \bibinfo{title}{Historical genomics of north american maize}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{109}}, \bibinfo{pages}{12420--12425}
  (\bibinfo{year}{2012}).

\bibitem{beissinger2014}
\bibinfo{author}{Beissinger, T.~M.} \emph{et~al.}
\newblock \bibinfo{title}{A genome-wide scan for evidence of selection in a
  maize population under long-term artificial selection for ear number}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{196}},
  \bibinfo{pages}{829--840} (\bibinfo{year}{2014}).

\bibitem{eyre2007}
\bibinfo{author}{Eyre-Walker, A.} \& \bibinfo{author}{Keightley, P.~D.}
\newblock \bibinfo{title}{The distribution of fitness effects of new
  mutations}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Genetics}}
  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{610--618}
  (\bibinfo{year}{2007}).

\bibitem{wallace2014}
\bibinfo{author}{Wallace, J.}, \bibinfo{author}{Larsson, S.} \&
  \bibinfo{author}{Buckler, E.}
\newblock \bibinfo{title}{Entering the second century of maize quantitative
  genetics}.
\newblock \emph{\bibinfo{journal}{Heredity}} \textbf{\bibinfo{volume}{112}},
  \bibinfo{pages}{30--38} (\bibinfo{year}{2014}).

\bibitem{weber2008}
\bibinfo{author}{Weber, A.~L.} \emph{et~al.}
\newblock \bibinfo{title}{The genetic architecture of complex traits in
  teosinte (zea mays ssp. parviglumis): new evidence from association mapping}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{180}},
  \bibinfo{pages}{1221--1232} (\bibinfo{year}{2008}).

\bibitem{pyhajarvi2013}
\bibinfo{author}{Pyh{\"a}j{\"a}rvi, T.}, \bibinfo{author}{Hufford, M.~B.},
  \bibinfo{author}{Mezmouk, S.} \& \bibinfo{author}{Ross-Ibarra, J.}
\newblock \bibinfo{title}{Complex patterns of local adaptation in teosinte}.
\newblock \emph{\bibinfo{journal}{Genome biology and evolution}}
  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{1594--1609}
  (\bibinfo{year}{2013}).

\bibitem{sattath2011}
\bibinfo{author}{Sattath, S.}, \bibinfo{author}{Elyashiv, E.},
  \bibinfo{author}{Kolodny, O.}, \bibinfo{author}{Rinott, Y.} \&
  \bibinfo{author}{Sella, G.}
\newblock \bibinfo{title}{Pervasive adaptive protein evolution apparent in
  diversity patterns around amino acid substitutions in drosophila simulans}.
\newblock \emph{\bibinfo{journal}{PLoS genetics}} \textbf{\bibinfo{volume}{7}},
  \bibinfo{pages}{e1001302} (\bibinfo{year}{2011}).

\bibitem{williamson2014}
\bibinfo{author}{Williamson, R.} \emph{et~al.}
\newblock \bibinfo{title}{Evidence for widespread positive and negative
  selection in coding and conserved noncoding regions of capsella grandiflora.}
\newblock \emph{\bibinfo{journal}{PLoS genetics}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{e1004622--e1004622}
  (\bibinfo{year}{2014}).

\bibitem{hernandez2011}
\bibinfo{author}{Hernandez, R.~D.} \emph{et~al.}
\newblock \bibinfo{title}{Classic selective sweeps were rare in recent human
  evolution}.
\newblock \emph{\bibinfo{journal}{science}} \textbf{\bibinfo{volume}{331}},
  \bibinfo{pages}{920--924} (\bibinfo{year}{2011}).

\bibitem{pritchard2010genetics}
\bibinfo{author}{Pritchard, J.~K.}, \bibinfo{author}{Pickrell, J.~K.} \&
  \bibinfo{author}{Coop, G.}
\newblock \bibinfo{title}{The genetics of human adaptation: hard sweeps, soft
  sweeps, and polygenic adaptation}.
\newblock \emph{\bibinfo{journal}{Current Biology}}
  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{R208--R215}
  (\bibinfo{year}{2010}).

\bibitem{ross2009}
\bibinfo{author}{Ross-Ibarra, J.}, \bibinfo{author}{Tenaillon, M.} \&
  \bibinfo{author}{Gaut, B.~S.}
\newblock \bibinfo{title}{Historical divergence and gene flow in the genus
  zea}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{181}},
  \bibinfo{pages}{1399--1413} (\bibinfo{year}{2009}).

\bibitem{eyre2009estimating}
\bibinfo{author}{Eyre-Walker, A.} \& \bibinfo{author}{Keightley, P.~D.}
\newblock \bibinfo{title}{Estimating the rate of adaptive molecular evolution
  in the presence of slightly deleterious mutations and population size
  change}.
\newblock \emph{\bibinfo{journal}{Molecular biology and evolution}}
  \textbf{\bibinfo{volume}{26}}, \bibinfo{pages}{2097--2108}
  (\bibinfo{year}{2009}).

\bibitem{castelletti2014mite}
\bibinfo{author}{Castelletti, S.}, \bibinfo{author}{Tuberosa, R.},
  \bibinfo{author}{Pindo, M.} \& \bibinfo{author}{Salvi, S.}
\newblock \bibinfo{title}{A mite transposon insertion is associated with
  differential methylation at the maize flowering time qtl vgt1}.
\newblock \emph{\bibinfo{journal}{G3: Genes| Genomes| Genetics}}
  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{805--812}
  (\bibinfo{year}{2014}).

\bibitem{mao2015}
\bibinfo{author}{Mao, H.} \emph{et~al.}
\newblock \bibinfo{title}{A transposable element in a nac gene is associated
  with drought tolerance in maize seedlings}.
\newblock \emph{\bibinfo{journal}{Nature Communications}}
  \textbf{\bibinfo{volume}{6}} (\bibinfo{year}{2015}).

\bibitem{yang2013}
\bibinfo{author}{Yang, Q.} \emph{et~al.}
\newblock \bibinfo{title}{{CACTA}-like transposable element in {ZmCCT}
  attenuated photoperiod sensitivity and accelerated the postdomestication
  spread of maize}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{110}}, \bibinfo{pages}{16969--16974}
  (\bibinfo{year}{2013}).

\bibitem{fraser2013gene}
\bibinfo{author}{Fraser, H.~B.}
\newblock \bibinfo{title}{Gene expression drives local adaptation in humans}.
\newblock \emph{\bibinfo{journal}{Genome research}}
  \textbf{\bibinfo{volume}{23}}, \bibinfo{pages}{1089--1096}
  (\bibinfo{year}{2013}).

\bibitem{Halligan:2013ir}
\bibinfo{author}{Halligan, D.~L.} \emph{et~al.}
\newblock \bibinfo{title}{{Contributions of Protein-Coding and Regulatory
  Change to Adaptive Molecular Evolution in Murid Rodents}}.
\newblock \emph{\bibinfo{journal}{PLoS Genetics}} \textbf{\bibinfo{volume}{9}},
  \bibinfo{pages}{e1003995--14} (\bibinfo{year}{2013}).

\bibitem{kimura1984}
\bibinfo{author}{Kimura, M.}
\newblock \emph{\bibinfo{title}{The neutral theory of molecular evolution}}
  (\bibinfo{publisher}{Cambridge University Press}, \bibinfo{year}{1984}).

\bibitem{Gunther:2010gt}
\bibinfo{author}{G{\"u}nther, T.} \& \bibinfo{author}{Schmid, K.~J.}
\newblock \bibinfo{title}{{Deleterious amino acid polymorphisms in Arabidopsis
  thaliana and rice}}.
\newblock \emph{\bibinfo{journal}{Theoretical and Applied Genetics}}
  \textbf{\bibinfo{volume}{121}}, \bibinfo{pages}{157--168}
  (\bibinfo{year}{2010}).

\bibitem{renaut2015}
\bibinfo{author}{Renaut, S.} \& \bibinfo{author}{Rieseberg, L.~H.}
\newblock \bibinfo{title}{The accumulation of deleterious mutations as a
  consequence of domestication and improvement in sunflowers and other
  compositae crops}.
\newblock \emph{\bibinfo{journal}{Molecular biology and evolution}}
  \bibinfo{pages}{msv106} (\bibinfo{year}{2015}).

\bibitem{coventry2010}
\bibinfo{author}{Coventry, A.} \emph{et~al.}
\newblock \bibinfo{title}{Deep resequencing reveals excess rare recent variants
  consistent with explosive population growth}.
\newblock \emph{\bibinfo{journal}{Nature communications}}
  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{131} (\bibinfo{year}{2010}).

\bibitem{Mezmouk:2014es}
\bibinfo{author}{Mezmouk, S.} \& \bibinfo{author}{Ross-Ibarra, J.}
\newblock \bibinfo{title}{{The pattern and distribution of deleterious
  mutations in maize.}}
\newblock \emph{\bibinfo{journal}{G3 (Bethesda, Md.)}}
  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{163--171}
  (\bibinfo{year}{2014}).

\bibitem{eyre2010}
\bibinfo{author}{Eyre-Walker, A.}
\newblock \bibinfo{title}{Genetic architecture of a complex trait and its
  implications for fitness and genome-wide association studies}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{107}}, \bibinfo{pages}{1752--1756}
  (\bibinfo{year}{2010}).

\bibitem{do2015}
\bibinfo{author}{Do, R.} \emph{et~al.}
\newblock \bibinfo{title}{No evidence that selection has been less effective at
  removing deleterious mutations in europeans than in africans}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}
  \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{126--131}
  (\bibinfo{year}{2015}).

\bibitem{simons2014}
\bibinfo{author}{Simons, Y.~B.}, \bibinfo{author}{Turchin, M.~C.},
  \bibinfo{author}{Pritchard, J.~K.} \& \bibinfo{author}{Sella, G.}
\newblock \bibinfo{title}{The deleterious mutation load is insensitive to
  recent population history}.
\newblock \emph{\bibinfo{journal}{Nature genetics}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{220--224}
  (\bibinfo{year}{2014}).

\bibitem{gazave2013}
\bibinfo{author}{Gazave, E.}, \bibinfo{author}{Chang, D.},
  \bibinfo{author}{Clark, A.~G.} \& \bibinfo{author}{Keinan, A.}
\newblock \bibinfo{title}{Population growth inflates the per-individual number
  of deleterious mutations and reduces their mean effect}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{195}},
  \bibinfo{pages}{969--978} (\bibinfo{year}{2013}).

\bibitem{lohmueller2014}
\bibinfo{author}{Lohmueller, K.~E.}
\newblock \bibinfo{title}{The impact of population demography and selection on
  the genetic architecture of complex traits}.
\newblock \emph{\bibinfo{journal}{PLoS Genetics}} \textbf{\bibinfo{volume}{10}}
  (\bibinfo{year}{2014}).
